An equivalence of compositional frameworks

### 2019-05-07 EquivCompFrameworks_20180911kc.tex
commented out double functor G going in other direction...might add later

\begin{comment}
We can also define the part of the double equivalence $\mathbb{G} \colon F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.

@@

On the other hand, given a horizontal 1-cell $N$ in $F\mathbb{C}\textnormal{sp}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$x \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);
\end{tikzpicture}
\]
the horizontal 1-cell $\mathbb{G}(N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!_c L(I)$} (B)
(C) edge node[above]{$!_c L(O)$} (B);
\end{tikzpicture}
\]
and then the horizontal 1-cell $\mathbb{E} \mathbb{G}(N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1.5,0) {$R(x)$};
\node (C) at (3,0) {$c_2$};
\node (D) at (1.5,-0.5) {$x \in F(R(x))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B);
\end{tikzpicture}
\]
Then we have a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\mathbb{C}\textnormal{sp}$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (D) at (1.5,0.5) {$x \in F(R(x))$};
\node (D') at (1.5,-1.5) {$x \in F(c)$};
\node (A) at (0,0) {$c_1$};
\node (B) at (1.5,0) {$R(x)$};
\node (C) at (3,0) {$c_2$};
\node (A') at (0,-1) {$c_1$};
\node (B') at (1.5,-1) {$c$};
\node (C') at (3,-1) {$c_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B)
(A') edge node[above]{$I$} (B')
(C') edge node[above]{$O$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$e$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(e)(x) \to x$$
where 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(L(c_1))$};
\node (C) at (2.5,0) {$R(L(c))$};
\node (D) at (3.5,0) {$R(x)$};
\node (E) at (4.5,0) {$c$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\eta_{c_1}$} (B)
(B) edge node[above]{$R(L(I))$} (C)
(C) edge node[above]{$R(!_c)$} (D)
(D) edge node[above]{$e$} (E)
(A) edge[bend right] node [above]{$I$} (E);
\end{tikzpicture}
\]
commutes.
\end{comment}

>>>>

We can also define the part of the double equivalence $\mathbb{G} \colon F\mathbb{C}\textnormal{sp} \to {_L \mathbb{C} \textnormal{sp}(\mathsf{X})}$ which goes in the other direction: again, the object component of this double functor will be $\mathbb{G}_0 = \id_{\mathsf{A}}$.

@@

On the other hand, given a horizontal 1-cell $N$ in $F\mathbb{C}\textnormal{sp}$:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$c$};
\node (C) at (2,0) {$c_2$};
\node (D) at (1,-0.5) {$x \in F(c)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$I$} (B)
(C) edge node[above]{$O$} (B);
\end{tikzpicture}
\]
the horizontal 1-cell $\mathbb{G}(N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$L(c_1)$};
\node (B) at (1,0) {$x$};
\node (C) at (2,0) {$L(c_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$!_c L(I)$} (B)
(C) edge node[above]{$!_c L(O)$} (B);
\end{tikzpicture}
\]
and then the horizontal 1-cell $\mathbb{E} \mathbb{G}(N)$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1.5,0) {$R(x)$};
\node (C) at (3,0) {$c_2$};
\node (D) at (1.5,-0.5) {$x \in F(R(x))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B);
\end{tikzpicture}
\]
Then we have a 2-isomorphism $\epsilon_N \colon \mathbb{E} \mathbb{G} (N) \xrightarrow{\sim} N$ in $F\mathbb{C}\textnormal{sp}$ given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (D) at (1.5,0.5) {$x \in F(R(x))$};
\node (D') at (1.5,-1.5) {$x \in F(c)$};
\node (A) at (0,0) {$c_1$};
\node (B) at (1.5,0) {$R(x)$};
\node (C) at (3,0) {$c_2$};
\node (A') at (0,-1) {$c_1$};
\node (B') at (1.5,-1) {$c$};
\node (C') at (3,-1) {$c_2$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$R(!_c L(I))\eta_{c_1}$} (B)
(C) edge node[above]{$R(!_c L(O))\eta_{c_2}$} (B)
(A') edge node[above]{$I$} (B')
(C') edge node[above]{$O$} (B')
(A) edge node [left]{$1$} (A')
(B) edge node [left]{$e$} (B')
(C) edge node [left]{$1$} (C');
\end{tikzpicture}
\]
$$\iota \colon F(e)(x) \to x$$
where 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$c_1$};
\node (B) at (1,0) {$R(L(c_1))$};
\node (C) at (2.5,0) {$R(L(c))$};
\node (D) at (3.5,0) {$R(x)$};
\node (E) at (4.5,0) {$c$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\eta_{c_1}$} (B)
(B) edge node[above]{$R(L(I))$} (C)
(C) edge node[above]{$R(!_c)$} (D)
(D) edge node[above]{$e$} (E)
(A) edge[bend right] node [above]{$I$} (E);
\end{tikzpicture}
\]
commutes.
